---
title: "submission23"
author: "Shannon Rush"
date: "July 28, 2014"
output: pdf_document
---

Neural network fit with nnet, with tuned parameters using 40% validation

### Load and Source
```{r source}
    source("../helpers/predictions.R")
```
```{r load_packages}
    library(caret)
    library(plyr)
    library(nnet)
```
```{r load_data, cache=TRUE}
    train <- read.csv("../../data/original/training.csv")
    test <- read.csv("../../data/original/test.csv")
```

### Data Processing
```{r create_validation, cache=TRUE}
    set.seed(2233)
    training.indices <- createDataPartition(train$Label, p=0.6, list=F)
    predictors <- setdiff(names(train),c("EventId","Weight"))
    training <- train[training.indices, predictors]
    validation <<- train[-training.indices, predictors]
```

### Models

## Functions
```{r}
    FitNnet <- function(size=1, decay=0.1, maxit=100, abstol=1.0e-4, reltol=1.0e-8, seed=111, 
                        training, val) {
        set.seed(seed)
        fit <- nnet(Label~., data=training, size=size, decay=decay, maxit=maxit, abstol=abstol, reltol=reltol) 
        pred <- predict(fit, val, type="class")
        confusionMatrix(pred, val$Label)
    } 
```


## Defaults
```{r}
    nnet.fit <- nnet(Label~., data=training, size=1, decay=0, maxit=100, abstol=1.0e-4, reltol=1.0e-8) 
    val.pred <- predict(nnet.fit, validation, type="class")
    confusionMatrix(val.pred, validation$Label)
```

## Tuning Decay

.7056
```{r}
    nnet.fit2 <- nnet(Label~., data=training, size=1, decay=0.1, maxit=100, abstol=1.0e-4, reltol=1.0e-8) 
    val.pred2 <- predict(nnet.fit2, validation, type="class")
    confusionMatrix(val.pred2, validation$Label)
```
.7065
```{r}
    nnet.fit3 <- nnet(Label~., data=training, size=1, decay=0.2, maxit=100, abstol=1.0e-4, reltol=1.0e-8) 
    val.pred3 <- predict(nnet.fit3, validation, type="class")
    confusionMatrix(val.pred3, validation$Label)
```
.7166
```{r}
    nnet.fit4 <- nnet(Label~., data=training, size=1, decay=0.3, maxit=100, abstol=1.0e-4, reltol=1.0e-8) 
    val.pred4 <- predict(nnet.fit4, validation, type="class")
    confusionMatrix(val.pred4, validation$Label)
```
.7364
```{r}
    FitNnet(decay=0.4)
```
.7041
```{r}
    FitNnet(decay=0.5)
```
.6937

## Tuning MaxIt
```{r}
    FitNnet(decay=0.3, maxit=200)
```
.7556
```{r}
    FitNnet(decay=0.3, maxit=300)
```
.7555

## Tuning Size

### Size = 2
```{r}
    FitNnet(decay=0.3, maxit=300, size=2)
```
.7801

Didn't converge, increasing maxit
```{r}
    FitNnet(decay=0.3, maxit=400, size=2)
```
.7923
Didn't converge, increasing maxit again
```{r}
    FitNnet(decay=0.3, maxit=500, size=2, seed=454)
```
.8157

### Size = 3
```{r}
    FitNnet(decay=0.3, maxit=500, size=3, seed=455)
```
.7925
```{r}
    FitNnet(decay=0.3, maxit=1000, size=3, seed=455)
```
.7931
```{r}
    FitNnet(decay=0.2, maxit=1000, size=3, seed=455)
```
.7962
```{r}
    FitNnet(decay=0.1, maxit=1000, size=3, seed=455)
```
8.2
```{r}
    FitNnet(decay=0, maxit=1000, size=3, seed=455)
```
.7956
```{r}
    FitNnet(decay=0.4, maxit=1000, size=3, seed=455)
```
.7885
### Size = 4

```{r}
    FitNnet(decay=0.3, maxit=1000, size=4, seed=455)
```
0.8245
```{r}
    FitNnet(decay=0.3, maxit=1500, size=4, seed=455)
```
0.8246
```{r}
    FitNnet(decay=0.2, maxit=1500, size=4, seed=455)
```
.7975
```{r}
    FitNnet(decay=0.1, maxit=1500, size=4, seed=455)
```
.7932
```{r}
    FitNnet(decay=0.4, maxit=1500, size=4, seed=455)
```
.8222

### Size = 5
```{r}
    FitNnet(decay=0.3, maxit=1500, size=5, seed=455)
```
0.8246
```{r}
    FitNnet(decay=0.2, maxit=1500, size=5, seed=455)
```
.8263
```{r}
    FitNnet(decay=0.1, maxit=1500, size=5, seed=455)
```
.8267
```{r}
    FitNnet(decay=0, maxit=1500, size=5, seed=455)
```
.8225
```{r}
    FitNnet(decay=0.4, maxit=1500, size=5, seed=455)
```
.8274
```{r}
    FitNnet(decay=0.5, maxit=1500, size=5, seed=455)
```
.825

### size = 6

```{r}
    FitNnet(decay=0.3, maxit=1500, size=6, seed=455)
```
.8286

### size = 7
```{r}
    FitNnet(decay=0.3, maxit=1500, size=7, seed=455)
```
.8287
### size = 8
```{r}
    FitNnet(decay=0.3, maxit=1500, size=8, seed=455)
```
.8281
```{r}
    FitNnet(decay=0.3, maxit=2000, size=8, seed=455)
```
.83
### size = 9
```{r}
    FitNnet(decay=0.3, maxit=2000, size=9, seed=455)
```
.8322
### size = 10
```{r}
    FitNnet(decay=0.3, maxit=2000, size=10, seed=455)
```
.8337
### size = 12
```{r}
    FitNnet(decay=0.3, maxit=2000, size=12, seed=455)
```
.8352
```{r}
    FitNnet(decay=0.3, maxit=2500, size=12, seed=455)
```
.8367
### size = 14
```{r}
    FitNnet(decay=0.3, maxit=2500, size=14, seed=455)
```
.8363
### size = 16
```{r}
    FitNnet(decay=0.3, maxit=3500, size=16, seed=455)
```
.8375
```{r}
    FitNnet(decay=0.2, maxit=3500, size=16, seed=455)
```
.8342
```{r}
    FitNnet(decay=0.4, maxit=3500, size=16, seed=455)
```
.838
```{r}
    FitNnet(decay=0.5, maxit=3500, size=16, seed=455)
```
.8369
```{r}
    FitNnet(decay=0.45, maxit=3500, size=16, seed=455)
```
.834
### size = 18
```{r}
    FitNnet(decay=0.3, maxit=3500, size=18, seed=455)
```
.8374
```{r}
    FitNnet(decay=0.2, maxit=3500, size=18, seed=455)
```
.8365
```{r}
    FitNnet(decay=0.4, maxit=3500, size=18, seed=455)
```
.8356
### size = 20
```{r}
    FitNnet(decay=0.3, maxit=4000, size=20, seed=455)
```
.8342
## Train 90%, Validate 10%
```{r create_validation, cache=TRUE}
    set.seed(33)
    training.indices <- createDataPartition(train$Label, p=0.9, list=F)
    predictors <- setdiff(names(train),c("EventId","Weight"))
    training <- train[training.indices, predictors]
    validation <<- train[-training.indices, predictors]
```
```{r}
    FitNnet(decay=0.4, maxit=3500, size=16, seed=455, training=training, val=validation)
```
.8368
## Bag on 90% training

```{r}
        set.seed(111)
        fit1 <- nnet(Label~., data=training, size=16, decay=0.4, maxit=3500) 
        pred1 <- predict(fit1, validation, type="class")
```
```{r}
        set.seed(222)
        fit2 <- nnet(Label~., data=training, size=16, decay=0.4, maxit=3500) 
        pred2 <- predict(fit2, validation, type="class")
```
```{r}
        set.seed(333)
        fit3 <- nnet(Label~., data=training, size=16, decay=0.4, maxit=3500) 
        pred3 <- predict(fit3, validation, type="class")
```
```{r}
        set.seed(444)
        fit4 <- nnet(Label~., data=training, size=16, decay=0.4, maxit=3500) 
        pred4 <- predict(fit4, validation, type="class")
```
```{r}
        set.seed(555)
        fit5 <- nnet(Label~., data=training, size=16, decay=0.4, maxit=3500) 
        pred5 <- predict(fit5, validation, type="class")
```
```{r}
    pred <- data.frame(pred1, pred2, pred3, pred4, pred5)
    all.agree <- apply(pred, 1, function(x) all(x=="b")|all(x=="s"))
    sum(all.agree)/nrow(pred)
    max.votes <- apply(pred, 1, function(x) ifelse(sum(x=="b") > sum(x=="s"), "b", "s"))
    confusionMatrix(max.votes, validation$Label)
```
.8422

## Reducing Overfitting
### Limit abstol
```{r}
    FitNnet(decay=0.4, maxit=3500, size=16, seed=455)
```
.838
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=54, abstol=.01)
```
.8384
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=54, abstol=0.1)
```
.8384
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=54, abstol=1)
```
.8384
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=54, abstol=10)
```
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=54, abstol=100)
```
.8384
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=54, abstol=1000)
```
.8384
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=54, abstol=100000)
```
.7969
### Limit reltol
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=48, reltol=.1)
```
.6469
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=48, reltol=.01)
```
.6711
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=48, reltol=.001)
```
.6811
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=48, reltol=.0001)
```
.7095
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=48, reltol=.00001)
```
.8175
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=48, reltol=.000001)
```
.8392
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=3500, decay=0.4, seed=48, reltol=.0000001)
```
.8376
### Limit maxit
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=500, decay=0.4, seed=46)
```
.7944
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=1000, decay=0.4, seed=46)
```
.8325
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=1500, decay=0.4, seed=46)
```
.8367
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=2000, decay=0.4, seed=46)
```
.8388
```{r}
    FitNnet(training=training, val=validation, size=16, maxit=2500, decay=0.4, seed=46)
```
.839

## Test Predictions

Single NN 

```{r}
    set.seed(231)
    nn.fit1 <- nnet(Label~., data=train[,predictors], size=16, decay=0.4, maxit=3500) 
    nn.pred1 <- predict(nn.fit1, test, type="raw")
    nn.pred1.class <- predict(nn.fit1, test, type="class")
    unordered <- data.frame(EventId=test$EventId, s=nn.pred1, Class=nn.pred1.class)
    ordered <- arrange(unordered, s)
    final.prediction <- data.frame(EventId=ordered$EventId,RankOrder=1:550000,Class=ordered$Class)
    filename <- "submission23.csv"
    write.csv(final.prediction, file=filename, row.names=F, quote=F)  
```
.284707
```{r}
    set.seed(232)
    nn.fit1 <- nnet(Label~., data=train[,predictors], size=16, decay=0.4, maxit=3500) 
```
