---
title: "submission19"
author: "Shannon Rush"
date: "July 25, 2014"
output: pdf_document
---

Boosting RF with higher sample weight given when approaching P("s")=.5

## Load
```{r}
    library(randomForest)
    library(plyr)
```
```{r load_data}
    train <- read.csv("../../data/original/training.csv")
    test <- read.csv("../../data/original/test.csv")
```
```{r}
    predictors <- setdiff(names(train),c("EventId","Label","Weight"))
    n <- nrow(train)
```
## Functions

```{r}
    MeanDiff <- function(pred) {
        mean(abs(pred$b-pred$s))
    }

    Weights <- function(pred) {
        1-abs(1-(pred$s/.5))
    }

    PredClass <- function(pred) {
        apply(pred, 1, function(x) ifelse(x["b"] > x["s"], "b", "s"))
    }
```

## Models
Run an unsampled RF
```{r}
    set.seed(191)
    rf1 <- randomForest(x=train[,predictors], y=train$Label, do.trace=T)
```
Predict on test
```{r}
    pred.test1 <- predict(rf1, test, type="prob")
    pred.class1 <- PredClass(pred.test1)
```
Predict on train
```{r}
    pred.train1 <- predict(rf1, train, type="prob")
    pred.train1 <- as.data.frame(pred.train1)
```
```{r}
    MeanDiff(pred.train1)
```
0.819479

Get weights based on probabilities
```{r}
    w <- 1-abs(1-(pred.train1$s/.5))
```
Get a new training sample, picking those observations the last forest was more indecisive about more often
```{r}
    t <- train[sample(n, n, T, w),]
```
## RF2 

Run another RF with the new sample
```{r}
    set.seed(192)
    rf2 <- randomForest(x=t[,predictors], y=t$Label, do.trace=T)
```
Predict on test
```{r}
    pred.test2 <- predict(rf2, test, type="prob")
    pred.class2 <- PredClass(pred.test2)
```
Predict on train
```{r}
    pred.train2 <- as.data.frame(predict(rf2, train, type="prob"))
```

```{r}
    MeanDiff(pred.train2)
```
0.6209119
```{r}
    t <- train[sample(n, n, T, Weights(pred.train2)),]
```

### RF3

```{r}
    set.seed(193)
    rf3 <- randomForest(x=t[,predictors], y=t$Label, do.trace=T)
    pred.test3 <- predict(rf3, test, type="prob")
    pred.class3 <- PredClass(pred.test3)
    pred.train3 <- as.data.frame(predict(rf3, train, type="prob"))
    MeanDiff(pred.train3)
    t <- train[sample(n, n, T, Weights(pred.train3)),]
```
0.8115788

### RF4

```{r}
    set.seed(194)
    rf4 <- randomForest(x=t[,predictors], y=t$Label, do.trace=T)
    pred.test4 <- predict(rf4, test, type="prob")
    pred.class4 <- PredClass(pred.test4)
    pred.train4 <- as.data.frame(predict(rf4, train, type="prob"))
    MeanDiff(pred.train4)
    t <- train[sample(n, n, T, Weights(pred.train4)),]
```

### RF5

```{r}
    set.seed(195)
    rf5 <- randomForest(x=t[,predictors], y=t$Label, do.trace=T)
    pred.test5 <- predict(rf5, test, type="prob")
    pred.class5 <- PredClass(pred.test5)
    pred.train5 <- as.data.frame(predict(rf5, train, type="prob"))
    MeanDiff(pred.train5)
    t <- train[sample(n, n, T, Weights(pred.train5)),]
```

## Prediction
```{r}
    pred <- data.frame(pred.class1, pred.class2, pred.class3, pred.class4, pred.class5)
    all.agree <- apply(pred, 1, function(a) all(a=="b")|all(a=="s"))
    sum(all.agree)/nrow(pred)
    nrow(pred)-sum(all.agree)
```
```{r}
    max.votes <- apply(pred, 1, function(x) ifelse(sum(x=="b") > sum(x=="s"), "b", "s"))
    probs <- (pred.test1[,2] + pred.test2[,2] + pred.test3[,2] + pred.test4[,2] + pred.test5[,2])/5
    df <- data.frame(EventId=test$EventId,probs=probs,Class=max.votes)
    ordered.df <- arrange(df, probs)
    final.df <- data.frame(EventId=ordered.df$EventId, RankOrder=1:550000, Class=ordered.df$Class)
    write.csv(final.df, file="submission19.csv", row.names=F, quote=F)
```
2.91569
```{r}
    disagree <- test[-which(all.agree),]
    disagree.pred <- pred[-which(all.agree),]
    disagree.probs <- probs[-which(all.agree)]
    mean(disagree.probs)
```





## Questions

Do 10 ProbBoostedRFs outperform 5?



