Submission 4 - Single RF with further feature selection
========================================================
```{r load_previous, cache=TRUE}
    load("rf1.RData")
```
```{r load_data, cache=TRUE}
    train <- read.csv("../data/processed/processed_train.csv")
    test <- read.csv("../data/original/test.csv")
```
```{r explore_previous, cache=TRUE}
    require(randomForest)
    require(plyr)
    
    rf$importance
    
    # Mean Decrease Gini
    g <- importance(rf, type=2, scale=F)
    gini <- data.frame(variables=rownames(g),MeanDecreaseGini=g[1:nrow(g)], stringsAsFactors=F)
    arrange(gini, desc(MeanDecreaseGini))

    # Mean Decrease Accuracy
    a <- importance(rf, type=1, scale=F)
    accuracy <- data.frame(variables=rownames(a),MeanDecreaseAccuracy=a[1:nrow(a)], stringsAsFactors=F)
    arrange(accuracy, desc(MeanDecreaseAccuracy))
    
    include <- unique(c(gini$variables[1:10]), accuracy$variables[1:10])
    include
```
Including only the top 5 resulted in an increased OOB error rate. Trying the top 10.
```{r forest_10, cache=TRUE}
   rf10 <- randomForest(x=train[,include], y=train$Label)
```
```{r explore_rf10}
    rf10$err.rate
```
Top 10 does not improve the OOB error rate. What about the top 15?
```{r}
    include.15 <- unique(c(gini$variables[1:15]), accuracy$variables[1:15])
    include.15
```
```{r forest_15, cache=TRUE}
   rf15 <- randomForest(x=train[,include.15], y=train$Label)
```
```{r explore_rf15}
    rf15$err.rate
```
15 improves on 10 but still behind including all variables. Trying top 20.
```{r}
    include.20 <- unique(c(gini$variables[1:20]), accuracy$variables[1:20])
    include.20
```
```{r forest_20, cache=TRUE}
   rf20 <- randomForest(x=train[,include.20], y=train$Label)
```
```{r explore_rf20}
    rf20$err.rate
```
Trying one more with 25.
```{r}
    include.25 <- unique(c(gini$variables[1:25]), accuracy$variables[1:25])
    include.25
```
```{r forest_25, cache=TRUE}
   rf25 <- randomForest(x=train[,include.25], y=train$Label)
```
```{r explore_rf25}
    rf25$err.rate
```
Limiting features in this way with a single random forest does not improve on OOB error rate. 
No submission.

